Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-07 providence/sections/prov.tex
.

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, we do not have expressions relating the risks, and so \Minerva may be vulnerable to an adversary choosing round sizes.

>>>>

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, we do not have expressions relating the risks, and so \Minerva may be vulnerable to an adversary choosing round sizes \cite{usenix_minerva, arxiv_athena}.
